%-------------------------
% Resume in Latex
% Author : Pedro Castro
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[empty]{fullpage}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{4.1pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom%
\raggedright%
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule{} \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & #2 \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING----------
\begin{center}
	\textbf{\Huge Pedro Castro} \\ \vspace{6pt}
	\faMapMarker*{} \small Porto, Portugal $|$ \faPhone{} +351 913455559 \\ \vspace{2pt}
	\faEnvelope{} \href{mailto:falecompedroac@gmail.com}{\underline{falecompedroac@gmail.com}} $|$
	\faLinkedin{} \href{https://linkedin.com/in/peucastro}{\underline{linkedin.com/in/peucastro}} $|$
	\faGithub{} \href{https://github.com/peucastro}{\underline{github.com/peucastro}}
\end{center}

%-----------PROFILE-----------
\section{Profile}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
	      Informatics and Computing B.E. student at FEUP with a strong interest in problem-solving and algorithm design. \\
	      Passionate about learning new technologies and contributing to projects. Open-source supporter.
	      }}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart%

\resumeSubheading%
{Faculty of Engineering of the University of Porto}{Porto, Portugal}
{Bachelor in Informatics and Computing Engineering \href{https://www.up.pt/feup/en/study/bachelors-degree/undergraduate-programmes/feup/22841/}{\faLink}}{Sep 2022 – Present}
\resumeItem{Relevant Coursework:}
\resumeItemListStart%
\item Mathematical Analysis, Linear Algebra, Physics, Discrete Mathematics, Theory of
Computation, Programming.
\item Algorithms and Data Structures, Operating Systems, Software Engineering,
Databases, Web Development.
\item Compilers, Parallel and Distributed Computing, Artificial Intelligence,
Computer Security, Computer Graphics.\ \resumeItemListEnd%

\resumeSubHeadingListEnd%

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart%

\resumeSubheading%
{Member}{Oct 2024 – Present}
{NIAEFEUP \href{https://ni.fe.up.pt}{\faLink}}{Porto, Portugal}
\resumeItemListStart%
\resumeItem{Developing a mobile app in Flutter made for students to help them organize their academic life and schedule.}
\resumeItem{Developer of the College Student's Association website using Svelte, Tailwind CSS, Kotlin and Spring Boot.}
\resumeItemListEnd%

\resumeSubHeadingListEnd%

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart%

\resumeProjectHeading%
{{\textbf{Pacman} \href{https://github.com/peucastro/ldts-pacman}{\faLink}} $|$ \emph{Java, SOLID Principles}}{Dec 2024}
\resumeItemListStart%
\resumeItem{Developed a text-based adaptation of the classic Pac-Man game using Java.}
\resumeItem{Designed the project following SOLID principles for maintainability and scalability.}
\resumeItem{Implemented object-oriented programming (OOP) techniques to modularize game logic and improve code reusability.}
\resumeItemListEnd%

\resumeProjectHeading%
{{\textbf{Hotel Reservation Database} \href{https://github.com/peucastro/bd_project}{\faLink}} $|$ \emph{SQL, Database Design, Normalization}}{Nov 2024}
\resumeItemListStart%
\resumeItem{Designed and implemented a relational database schema for hotel room reservations.}
\resumeItem{Developed a SQL database to manage bookings, cancellations, and room availability efficiently.}
\resumeItem{Applied database normalization techniques to ensure data integrity and reduce redundancy.}
\resumeItemListEnd%

\resumeProjectHeading%
{{\textbf{Water Supply Management Analysis Tool} \href{https://github.com/peucastro/DA2324_PRJ1_G184}{\faLink}} $|$ \emph{Max-Flow Graph Algorithms}}{Apr 2024}
\resumeItemListStart%
\resumeItem{Developed a graph-based tool to assist the Management Team of a water supply network in Portugal.}
\resumeItem{Implemented Max-Flow Graph Algorithms to analyze network metrics, evaluate resilience and optimize resource allocation.}
\resumeItem{Provided data-driven insights for resource allocation and identified potential improvements.}
\resumeItemListEnd%

\resumeProjectHeading%
{{\textbf{L.EIC Schedules Management System} \href{https://github.com/peucastro/aed_project}{\faLink}} $|$ \emph{Schedule Management, Sorting, Searching}}{Nov 2023}
\resumeItemListStart%
\resumeItem{Created a system for managing a course schedule efficiently.}
\resumeItem{Integrated algorithms for modifying, searching, viewing, sorting, and listing schedules.}
\resumeItem{Designed an intuitive CLI interface for improved accessibility and usability.}
\resumeItemListEnd%

\resumeProjectHeading%
{{\textbf{Image Editing Program} \href{https://github.com/peucastro/prog_project}{\faLink}} $|$ \emph{C++, CLI, Image Processing}}{May 2023}
\resumeItemListStart%
\resumeItem{Developed a simple C++ command-line tool for image manipulation tasks.}
\resumeItem{Implemented key features such as cropping, mirroring, inverting, and pasting images.}
\resumeItemListEnd%

\resumeSubHeadingListEnd%

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
	      \textbf{Programming Languages}{: C, C++, RISC-V Assembly, Java, Python, SQL, HTML, CSS, JavaScript, Dart} \\
	      \textbf{Frameworks}{: JUnit, Mockito, Flutter, Vue.js} \\
	      \textbf{Software Development}{: Object-Oriented Programming, Software Architecture, Design Patterns, Refactoring, Unit Testing, Debugging, Linux, Git} \\
	      \textbf{Algorithms and Data Structures}{: Algorithm Analysis, Algorithm Design, Graph Algorithms} \\
	      \textbf{Databases and Data Analysis}{: SQLite, PostgreSQL, MySQL, Pandas, Relational Algebra, Database Design}
	      }}
\end{itemize}

%-----------LANGUAGES-----------
\section{Languages}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
	      \textbf{Portuguese}{: Native} $|$
	      \textbf{English}{: Highly Proficient}
	      }}
\end{itemize}

%-------------------------------------------
\end{document}
